# Calculate the control values (Blank, Live cells, DMSO)

We can use the function `mean()` to calculate the average of a set of numbers. 
We can use `$` to select the column of our dataframe, and `[1:3]` to select rows 1-3 (or any numbers). 

## Calculating the blank

If both rows of the blank are media only (Blank_L and Blank_R) you can calculate the blank with the line: 

```{r}
#| eval: false
Blank_Average <- mean(mean(raw_data$Blank_L), mean(raw_data$Blank_R))
```

If you have some of your wells as a media and drug control, we can calculate the blank values separately for the different controls: 

```{r}
#| eval: false
# Media only control in rows 1-3 of Blank_L
Blank_Average <- mean(raw_data$Blank_L[1:3])

# If you have a media + drug (no cells control), e.g. in rows 4-6 of Blank_L
Media_drug1_control <- mean(raw_data$Blank_L[4:6])
```

## Calculating the Live/ DMSO controls 

You can then calculate the Live and DMSO controls using these: 

```{r}
#| eval: false
# Calculate Live cells average  (Live.DMSO rows 1-3)
Live_cells <- mean(raw_data$Live.DMSO[1:3]) - Blank_Average

# Calculate DMSO control average (Live.DMSO rows 4-6)
DMSO_cells <- mean(raw_data$Live.DMSO[4:6]) - Blank_Average
```